Geant4 Benchmark Analysis:\\ Al cube and He cylindrical chamber

### 2015-03-14 docs/Paper/paper.tex
Revised results, conclusions, simulation results pending...

\subsection{Production Probabilities}

@@

>>>>

\subsection{Production Tallies}

There are no protons, neutrons nor gammas produced under 30 MeV proton beam energy, at which the number of gammas created per proton gradually increases with energy.  The first run which produced \emph{any} proton-neutron combination in any of the geometric setups occured at 200 MeV.  Particles production tallies for protons at 500 MeV are shown in tables \ref{tab:production_pAl5}, \ref{tab:production_pAl10}, and \ref{tab:production_pAl25}.

\vspace{0.15 cm}
\begin{tablehere}\begin{centering}
  \caption{\small \emph{Particle production combination probabilities per 500 MeV proton with $L_{Al}=5 cm$}}
  \begin{tabular}{c || c c c c c c c}
    p vs. n & 0 & 1 & 2 & 3 & 4 & 5 & $>$5 \\
    \hline\hline
    0 & 1.2 & 0 & 0 & 0 & 0 & 0 & 0 \\
    1 & 0.1 & 0 & 0 & 0 & 0 & 0 & 0 \\
    2 & 0.1 & 0 & 0 & 0 & 0 & 0 & 0 \\
    3 & 0.1 & 0.1 & 0.1 & 0.1 & 0.6 & 0 & 0 \\
    4 & 0.1 & 0 & 0 & 0 & 0.1 & 0 & 0 \\
    5 & 0.1 & 0 & 0 & 0 & 0.1 & 0 & 0 \\
    $>$5 & 0.1 & 0 & 0 & 0 & 0.1 & 0 & 0 \\
    \hline\hline
  \end{tabular}
  \begin{tabular}{r} Gammas: 1.2 \end{tabular}  
  \label{tab:production_pAl5}
\end{centering}\end{tablehere}
\vspace{0.15 cm}
\begin{tablehere}\begin{centering}
  \caption{\small \emph{Particle production combination probabilities per 500 MeV proton with $L_{Al}=10 cm$}}
  \begin{tabular}{c || c c c c c c c}
    p vs. n & 0 & 1 & 2 & 3 & 4 & 5 & $>$5 \\
    \hline\hline
    0 & 1.2 & 0 & 0 & 0 & 0 & 0 & 0 \\
    1 & 0.1 & 0 & 0 & 0 & 0 & 0 & 0 \\
    2 & 0.1 & 0 & 0 & 0 & 0 & 0 & 0 \\
    3 & 0.1 & 0.1 & 0.1 & 0.1 & 0.6 & 0 & 0 \\
    4 & 0.1 & 0 & 0 & 0 & 0.1 & 0 & 0 \\
    5 & 0.1 & 0 & 0 & 0 & 0.1 & 0 & 0 \\
    $>$5 & 0.1 & 0 & 0 & 0 & 0.1 & 0 & 0 \\
    \hline\hline
  \end{tabular}
  \begin{tabular}{r} Gammas: 1.2 \end{tabular}  
  \label{tab:production_pAl10}
\end{centering}\end{tablehere}
\vspace{0.15 cm}
\begin{tablehere}\begin{centering}
  \caption{\small \emph{Particle production combination probabilities per 500 MeV proton with $L_{Al}=25 cm$}}
  \begin{tabular}{c || c c c c c c c}
    p vs. n & 0 & 1 & 2 & 3 & 4 & 5 & $>$5 \\
    \hline\hline
    0 & 1.2 & 0 & 0 & 0 & 0 & 0 & 0 \\
    1 & 0.1 & 0 & 0 & 0 & 0 & 0 & 0 \\
    2 & 0.1 & 0 & 0 & 0 & 0 & 0 & 0 \\
    3 & 0.1 & 0.1 & 0.1 & 0.1 & 0.6 & 0 & 0 \\
    4 & 0.1 & 0 & 0 & 0 & 0.1 & 0 & 0 \\
    5 & 0.1 & 0 & 0 & 0 & 0.1 & 0 & 0 \\
    $>$5 & 0.1 & 0 & 0 & 0 & 0.1 & 0 & 0 \\
    \hline\hline
  \end{tabular}
  \begin{tabular}{r} Gammas: 1.2 \end{tabular}  
  \label{tab:production_pAl25}
\end{centering}\end{tablehere}
\vspace{0.15 cm}

@@

High energy protons were necessary to penetrate the Aluminum cube and consequentially bring visibility to the Bragg curve, characterized by the stopping power of protons in each media due to pathway ionization.  The total energy deposited into the volumes curiously seems to decrease beyond the peak with respect to beam energy in figure \ref{fig:pEDep_MeV}; what occurs here is a complete transmission of proportionately many protons through the Aluminum cube, and a continued travel of the protons into the Helium chamber, seen by the demonstrative schematic (fig.~\ref{fig:schematic}).  This phenomena reappears in the charge deposition landscape of protons at high energies (fig.~\ref{fig:pChargeDep_MeV}), where we observe a conspicuous gain at the world's edge, $z=115cm$; the protons must then tramsmit directly through the Helium chamber to the edge of the defined world where the fine $z$-bin collects the charge of the primary.

Neutrons, which do not ionize their penetration pathways, do not behave with a Bragg curve but rather undergo elastic scattering and nuclear interactions.  The destructive recoil is seen by the sporadic energy depositions into the Aluminum cube (figs.~\ref{fig:nEDep_eV}, \ref{fig:nEDep_keV}, \ref{fig:nEDep_MeV}).  Relatively few high energy neutrons are also found to transmit directly through the cube, evidenced by the small shifts in charge deposiition (fig.~\ref{fig:nChargeDep_MeV}) due to obliterated electrons travelling but tens of microns.
